The mapmisc package

### 2013-11-18 pkg/mapmisc/inst/doc/mapmisc.rnw
changed results of colourScale to plot, col, colOpacity, also made methods for factors, rasters
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@629 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Create a colour scale for plotting copper  concentrations
<<meuseScale>>=
cuScale = colourScale(meuse$copper, breaks=5, style='equal', 
		opacity=0.8, dec=-1, firstBreak=0)
@
and elevation, with transparency decreasing as elevation increases.
<<elevScale>>=
elevScale = colourScale(values(nldElev), breaks=6, col=terrain.colors,
		firstBreak=0, dec=-1,opacity=c(0.2, 0.9))
@
Soil type is a categorical variable, create a factor and create a colour scale
of unique values
<<soilScale>>=
meuse$soilFac = factor(meuse$soil, levels=c(1,2,3), 
		labels=c("Calcareous","Non-Calc's","Red Brick"))
soilScale = colourScale(meuse$soilFac, style="unique",
		col="Set2")
@

<<meuseLegends,fig.subcap=c("Copper","soil", "elevation"), fig.cap="Meuse data again">>=
map.new(meuse)
plot(nldTiles, add=TRUE)
plot(meuse, col=cuScale$col,add=TRUE,pch=16)
scaleBar(meuse, pos="topleft",bg="white")
legendBreaks("bottomright",  breaks=cuScale,
		title="gals/firkin",bg="white",adj=c(0,-2))

map.new(meuse)
plot(nldTiles, add=TRUE)
plot(meuse, col=soilScale$col,add=TRUE,pch=16)
scaleBar(meuse, pos="topleft",bg="white")
legend("bottomright", fill=soilScale$legendCol, legend=soilScale$breaks,
		title="soil type", cex=0.7,bg="white")

map.new(meuse)
plot(nldTiles, add=TRUE)
image(nldElev, breaks=elevScale$breaks, col=elevScale$withTrans, legend=FALSE,add=TRUE)
scaleBar(meuse, pos="topleft",bg="white")
legendBreaks("left", breaks=elevScale, title='Metres',bg="white")
@

>>>>

Create a colour scale for plotting copper  concentrations
<<meuseScale>>=
cuScale = colourScale(meuse$copper, breaks=5, style='equal', 
		opacity=0.8, dec=-1, firstBreak=0)
@
and elevation, with transparency decreasing as elevation increases.
<<elevScale>>=
elevScale = colourScale(nldElev, style='equal',
		breaks=6, col=terrain.colors,
		firstBreak=0, dec=-1,opacity=c(0.2, 0.9))
@
Soil type is a categorical variable, create a factor and create a colour scale
of unique values
<<soilScale>>=
meuse$soilFac = factor(meuse$soil, levels=c(1,2,3), 
		labels=c("Calcareous","Non-Calc's","Red Brick"))
soilScale = colourScale(meuse$soilFac, style="unique",
		col="Set2")
@

<<meuseLegends,fig.subcap=c("Copper","soil", "elevation"), fig.cap="Meuse data again">>=
map.new(meuse)
plot(nldTiles, add=TRUE)
plot(meuse, col=cuScale$plot,add=TRUE,pch=16)
scaleBar(meuse, pos="topleft",bg="white")
legendBreaks("bottomright",  breaks=cuScale,
		title="gals/firkin",bg="white",adj=c(0,-2))

map.new(meuse)
plot(nldTiles, add=TRUE)
plot(meuse, col=soilScale$plot,add=TRUE,pch=16)
scaleBar(meuse, pos="topleft",bg="white")
legendBreaks("bottomright", breaks=soilScale,
		title="soil type", cex=0.7,bg="white")

map.new(meuse)
plot(nldTiles, add=TRUE)
image(nldElev, breaks=elevScale$breaks, col=elevScale$colOpacity, 
		legend=FALSE,add=TRUE)
scaleBar(meuse, pos="topleft",bg="white")
legendBreaks("left", breaks=elevScale, title='Metres',bg="white")
@
